---
title: "Excersice Sheet 6"
fontsize: 11pt
header-includes: \usepackage[german]{babel}
output:
  pdf_document:
    highlight: haddock
  html_document: default
fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      eval = TRUE,
                      warning = FALSE,
                      message = FALSE)
```

_What factors explain excessive alcohol consumption among students?_ The record for the task sheet comes from a survey of students who attended mathematics and Portuguese courses and contains many interesting details about their sociodemographics, life circumstances and learning success.  
The ordinal scaled variables `Dalc` and `Walc` give information about the alcohol consumption of the students on weekdays and weekends. Create a binary target variable `alc_prob` as follows:

```{r, echo=T, eval=T}
library(stringr)
library(readr)
library(dplyr)
# (Adapt Path)
 StudentDF <- read_csv(str_c(dirname(getwd()), "/Exercise6/student_alc.csv"))
 
 gain.function <- function(GiniTar,s_var){
  g = GiniTar - s_var
  return(g)
}
 Ginni.function <- function(DF){
  p <<- (apply(DF, 2, function(i) i/sum(i)))
  Gin <- 1- (sum(p*p))

  return(Gin)
}
main.function<- function(df){
  StudentDF <<- df %>% mutate(alc_prob = ifelse(Dalc + Walc >= 6, "alc_p" , "no_alc_p" ))
  colnames(StudentDF)[ncol(StudentDF)] <- "TargVar"
  TargetList <- as.data.frame(table(StudentDF$TargVar))
  TargetList <- data.frame(TargetList[,-1], row.names = TargetList[,1])
  GiniTar <- Ginni.function(TargetList)
  Student_alc_prob = subset(StudentDF, select= -c(TargVar))
  GiniGainList = list()
  gini_var <- 0
  for (Var in (names(Student_alc_prob))) {
    var_df <-count(StudentDF,StudentDF[[Var]],StudentDF$TargVar)
    for (var_val in unique(var_df[[1]])) {
      temp_df <- subset(var_df,var_df[[1]]==var_val)
      a<- dim(StudentDF)
      Probablity <- sum(temp_df$n)/a[1]
      filtered_df = subset(temp_df, select= -c(1:2))
      gini_val <- Ginni.function(filtered_df)*Probablity
      gini_var <- gini_var+ gini_val
    }
    gini_gain <- gain.function(GiniTar,gini_var)
    GiniGainList[[Var]] <- gini_gain
    gini_var <- 0
    gini_val<- 0
    gini_gain<-0
    
  }
  
  TotalGinni<- do.call(rbind, GiniGainList)
}

main.function(StudentDF)
```

1. Calculate the Gini index for the target variable `alc_prob` and the _Gini index_ for each variable with respect to `alc_prob`. Determine the 5 variables with the highest _Gini Gain_.

```{r}
# Solution for Task 1
```

2. Learn 2 different decision trees with `alc_prob` as target variable. For the first tree, nodes should be further partitioned until the class distribution of all resulting leaf nodes is pure. For the second tree, nodes with a cardinality of less than 20 instances should not be further partitioned. Determine the quality of the trees by calculating sensitivity (_True Positive Rate_) and specificity (_True Negative Rate_) for a 70%:30% split in training and test sets. Display the decision trees graphically and discuss the differences in quality measures

```{r}
# Solution for Task 2
```

3. Use `randomForest::randomForest()` to create a random forest with 200 trees. As candidates for a split within a tree a random sample of 5 variables should be drawn. Calculate Accuracy, Sensitivity and Specificity for the Out-of-the-Bag instances and show the most important variables (`?importance`).

```{r}
# Solution for Task 3
```
------
Dataset: http://isgwww.cs.uni-magdeburg.de/cv/lehre/VisAnalytics/material/exercise/datasets/student_alc.csv  
(Source: https://www.kaggle.com/uciml/student-alcohol-consumption)